---
output: 
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggcircumscribe

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

ggcircumscribe is a ggplot2 extension for fitting text into circles. It is derived from [ggfittext](https://wilkox.org/ggfittext). The inspiration was [the need to label circles in ggcirclepack](https://github.com/teunbrand/ggplot-extension-club/discussions/15).

## Installation

You can install the development version of ggcircumscribe from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wilkox/ggcircumscribe")
```

ggcircumscribe is not yet on CRAN.

## Example

ggcircumscribe currently provides only one geom, `geom_circumscribe()`. The radius of the circle in which the text is to be drawn is currently set as an absolute `grid::unit()` value; this is likely to change in future as use cases for the package are more clearly defined.

```{r example}
library(ggplot2)
library(ggcircumscribe)

example_data <- data.frame(
  time = c(3, 5, 7),
  space = c(3, 5, 7),
  observation = c("Early morning joggers", "A baby kookaburra wearing a gown", "Cake")
)

ggplot(example_data, aes(x = time, y = space, label = observation)) +
  geom_abs_circle(radius = grid::unit(20, "mm")) +
  geom_circumscribe(radius = grid::unit(20, "mm"), grow = TRUE) +
  scale_x_continuous(limits = c(0, 10)) +
  scale_y_continuous(limits = c(0, 10))
```

## Roadmap

Currently planned features and changes:

- Implement 'reflow' parameter
- Change reflowing algorithm to optimise for a circle rather than a square
- Support angled text
- Add tests
